Searching for flaring star-planet interactions in star-planet systems in Kepler and TESS

### 2023-02-01 src/tex/ms.tex
[showyourwork] overleaf sync

We complemented the PSCP with the TESS TOI Table~\citep[TT][]{guerrero2021arxiv}\footnote{\url{https://tev.mit.edu/data/collection/193/}}. We filtered the catalog by requiring the confirmed planet (CP) or known planet (KP) flags to be set in the ``TOI Disposition''. This added XXXX star-planet systems to the sample.
\subsection{Multiplicity}
We flag all multiple stars except for Proxima Cen (whose companion are well separated both physically and on the sky), but kept them in for the analysis. In addition to noting the multiplicity of some well-known stars, we also use the Robo-AO catalog of nearby companions to Kepler planet candidates from ~\cite{ziegler2018measuring}

@@

\subsection{X-ray luminosity}
We take the \cite{foster2022exoplanet} X-ray luminosity catalog as the basis for our calculation, assuming an uncertainty of 30\% in the reported values, covering typical intrinsic variability among stars of similar rotation periods in studies like ~\cite{wright2011stellaractivityrotation, wright2018stellar}.

@@

Table XXXX shows

>>>>

We complemented the PSCP with the TESS TOI Table~\citep[TT][]{guerrero2021arxiv}\footnote{\url{https://tev.mit.edu/data/collection/193/}}. We filtered the catalog by requiring the confirmed planet (CP) or known planet (KP) flags to be set in the ``TOI Disposition''. This added XXXX star-planet systems to the sample.
\subsection{Multiplicity and contamination}
We drop all multiple stars except for Proxima Cen (whose companion are well separated both physically and on the sky), and all stars with nearby objects that contaminate our analysis, e.g., from ~\citet{ziegler2018measuring}.

Quoting the references for multiplicity/contamination, we dropped the following targets: \input{output/multiples_string.tex}

@@

\subsection{Bolometric luminosity}

We take bolometric luminosity values as given in the NASA Table if given with uncertainties, and supplement missing values and entries without quoted uncertainties with Gaia DR3 FLAME~\citep{fouesneau2022gaia} solutions.

% \subsection{X-ray luminosity}
% We take the \cite{foster2022exoplanet} X-ray luminosity catalog as the basis for our calculation, assuming an uncertainty of 30\% in the reported values, covering typical intrinsic variability among stars of similar rotation periods in studies like ~\cite{wright2011stellaractivityrotation, wright2018stellar}.

@@

\begin{table*}
\movetableright=-20mm
\footnotesize
    \script{paper_main_table.py}
    \caption{Star-planet systems.}
    \input{output/table_lit_vals.tex}
        \label{tab:maintable_lit}
    \tablerefs{\input{output/lit_table_bibstring.tex}}
\end{table*}

\begin{table*}
\movetableright=-20mm
    \script{paper_main_table.py}
    \caption{Flaring SPI results.}
    \input{output/table_der_vals.tex}
        \label{tab:maintable_der}

\end{table*}
